Automatic Matching of Bullet Lands

### 2016-01-03 imaging-paper.Rnw
Update to be compatible with new processBullets

lof <- processBullets(paths = images[c(5,7)], x = 100)

subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y + 23*1.5625 # working now!!!
lofX <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

lof <- processBullets(paths = images[c(5,7)], x = 100)

subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y - min(subLOFx1$y)
subLOFx2$y <- subLOFx2$y - min(subLOFx2$y)
ccf <- ccf(subLOFx1$resid, subLOFx2$resid, lag.max=100, plot=FALSE)
lag <- ccf$lag[which.max(ccf$acf)]
subLOFx1$y <- subLOFx1$y - lag*1.5625 
lofY <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

\begin{figure}[hbtp]
\centering
    \begin{subfigure}[t]{\textwidth}\centering
\caption{Loess smooth of signatures  at $x = 100$ (span is 0.03).\label{fig:smooth}}{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='.65\\textwidth', warning=FALSE>>=
qplot(data=lofX, y, resid, colour=I("grey30"), size=I(0.75), geom="line", group=bullet) +
  geom_line(aes(y=l30), colour="grey70", size=0.5) +
  facet_grid(bullet~.) +
#  scale_colour_manual("", values=cols) +
  theme_bw() + ylab("") + 
  theme(legend.position="none")
@
    }
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{Using a rolling median peaks and valleys are identified for each signature. Peaks and valleys on the signature correspond to striation marks on the bullet's surface. \label{fig:smoothcutb}}{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='.65\\textwidth', warning=FALSE>>=
#images <- file.path(datadir, dir(datadir))
  lof <- processBullets(paths = images[c(5,7)], x = 100)
  lof <- bulletSmooth(lof)
  bAlign = bulletAlign(lof)
  lofX <- bAlign$bullet

@@

\begin{figure}[hbtp]
  \centering
<<crosscuts-vary-b31, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100,250, by=25)
lof <- processBullets(paths[37], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

>>>>

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read.x3p(images[5]), name = images[5], x = 100)
subLOFx2 <- processBullets(read.x3p(images[7]), name = images[7], x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y + 23*1.5625 # working now!!!
lofX <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read.x3p(images[5]), name = images[5], x = 100)
subLOFx2 <- processBullets(read.x3p(images[7]), name = images[7], x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y - min(subLOFx1$y)
subLOFx2$y <- subLOFx2$y - min(subLOFx2$y)
ccf <- ccf(subLOFx1$resid, subLOFx2$resid, lag.max=100, plot=FALSE)
lag <- ccf$lag[which.max(ccf$acf)]
subLOFx1$y <- subLOFx1$y - lag*1.5625 
lofY <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

\begin{figure}[hbtp]
\centering
    \begin{subfigure}[t]{\textwidth}\centering
\caption{Loess smooth of signatures  at $x = 100$ (span is 0.03).\label{fig:smooth}}{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='.65\\textwidth', warning=FALSE>>=
qplot(data=lofX, y, resid, colour=I("grey30"), size=I(0.75), geom="line", group=bullet) +
  geom_line(aes(y=l30), colour="grey70", size=0.5) +
  facet_grid(bullet~.) +
#  scale_colour_manual("", values=cols) +
  theme_bw() + ylab("") + 
  theme(legend.position="none")
@
    }
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{Using a rolling median peaks and valleys are identified for each signature. Peaks and valleys on the signature correspond to striation marks on the bullet's surface. \label{fig:smoothcutb}}{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='.65\\textwidth', warning=FALSE>>=
#images <- file.path(datadir, dir(datadir))
  #lof <- processBullets(paths = images[c(5,7)], x = 100)

  subLOFx1 <- processBullets(read.x3p(images[5]), name = images[5], x = 100)
  subLOFx2 <- processBullets(read.x3p(images[7]), name = images[7], x = 100)
  lof <- rbind(subLOFx1, subLOFx2)

  lof <- bulletSmooth(lof)
  bAlign = bulletAlign(lof)
  lofX <- bAlign$bullet

@@

\begin{figure}[hbtp]
  \centering
<<crosscuts-vary-b31, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100,250, by=25)
lof <- processBullets(read.x3p(paths[37]), name = paths[37], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)
